More than one Author with different Affiliations

### 2016-04-13 NatPlant2/manuscript.tex
minor changes

The absence of evidence for a genome-wide impact of hard sweeps in coding regions differs markedly from observations in \emph{Drosophila} \cite{sattath2011} and \emph{Capsella} \cite{williamson2014}, but is consistent with data from humans \cite{hernandez2011}.
Comparisons of the estimated percentages of nonsynonmyous substitutions fixed by natural selection \cite{ross2009,sella2009,eyre2009estimating,williamson2014} give similar results. 
While differences in long-term $N_e$ likely explains some of the observed variation across species, we see little change in the importance of hard sweeps in genes in singleton diversity in modern maize (Figure \ref{sFig:singleton}), perhaps suggesting other factors may contribute to these differences as well.  
One possibility, for example, is that, if mutational target size scales with genome size, the larger genomes of human and maize may offer more opportunities for noncoding loci to contribute to adaptation, with hard sweeps on nonsynonymous variants then playing a relatively smaller role. 
Support for this idea comes from numerous cases of adaptive transposable element insertion modifying gene regulation in maize \cite{studer2011,mao2015,yang2013} and studies of local adaptation that show enrichment for SNPs in regulatory regions in teosinte \cite{pyhajarvi2013} and humans \cite{fraser2013gene} but for nonsynonymous variants in the smaller \emph{Arabidopsis} genome.  
Our results, for example, are not dissimilar to findings in the comparably-sized mouse genome, where no differences are seen in diversity around nonsynonymous and synonymous substitutions in spite of a large $N_e$ and  as many as 80\% of adaptive substitutions occuring outside of genes\cite{Halligan:2013ir}.
Future comparative analyses using a common statistical framework (e.g. \cite{corbett2015} )and considering additional ecological and life history factors (c.f. \cite{leffler2012}) should allow explicit testing of this idea.

\subsection*{Demography influences the efficiency of purifying selection} %JRI 
One of our more striking findings is that the impact of purifying selection on maize and teosinte qualitatively changed over time. 
We observe a more pronounced decrease in $\pi$ around genes in teosinte than maize (Figure \ref{fig:purify}A), but the opposite trend when we evaluate diversity using singleton polymorphisms (Figure \ref{fig:purify}B).
The efficiency of purifying selection is proportional to effective population size \cite{kimura1984}, and these results are thus consistent with our demographic analyses which show a domestication bottleneck and smaller long-term $N_e$ in maize \cite{eyre1998, tenaillon2004, wright2005, ross2009} followed by recent rapid expansion and a much larger modern $N_e$. 
Simple foward-in-time population genetic simulations qualitatively confirm these results, and further suggest that the observed patterns are likely cause by sites under relatively weak purifying selection \ref{sFig:sims}.

Although demographic change affects the efficiency of purifying selection, it may have limited implications for genetic load. 
Recent population bottlenecks and expansions have increased the relative abundance of rare and 
deleterious variants in domesticated plants \cite{renaut2015} and human populations out of Africa \cite{keinan2012,coventry2010}, and such variants may play an important role in phenotypic variation \cite{Mezmouk:2014es, coventry2010, eyre2010}.
Nonetheless, demographic history may have little impact on the overall genetic load of populations \cite{do2015,simons2014}, as decreases in $N_e$ that allow weakly deleterious variants to escape selection also help purge strongly deleterious ones, and the increase of new deleterious mutations in expanding populations is mitigated by their lower initial frequency and the increasing efficiency of purifying selection \cite{simons2014, lohmueller2014}.

@@

\section*{ACKNOWLEDGEMENTS}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.

>>>>

The absence of evidence for a genome-wide impact of hard sweeps in coding regions differs markedly from observations in \emph{Drosophila} \cite{sattath2011} and \emph{Capsella} \cite{williamson2014}, but is consistent with data from humans \cite{hernandez2011}.
Comparisons of the estimated percentages of nonsynonmyous substitutions fixed by natural selection \cite{ross2009,sella2009,eyre2009estimating,williamson2014} give similar results. 
While differences in long-term $N_e$ likely explains some of the observed variation across species, we see little change in the importance of hard sweeps in genes in singleton diversity in modern maize (Figure \ref{sFig:singleton}), perhaps suggesting other factors may contribute to these differences as well.  
One possibility, for example, is that, if mutational target size scales with genome size, the larger genomes of human and maize may offer more opportunities for noncoding loci to contribute to adaptation, with hard sweeps on nonsynonymous variants then playing a relatively smaller role. 
Support for this idea comes from numerous cases of adaptive transposable element insertion modifying gene regulation in maize \cite{studer2011,mao2015,yang2013} and studies of local adaptation that show enrichment for SNPs in regulatory regions in teosinte \cite{pyhajarvi2013} and humans \cite{fraser2013gene} but for nonsynonymous variants in the smaller \emph{Arabidopsis} genome \cite{hancock2011adaptation}.  
Our results, for example, are not dissimilar to findings in the comparably-sized mouse genome, where no differences are seen in diversity around nonsynonymous and synonymous substitutions in spite of a large $N_e$ and  as many as 80\% of adaptive substitutions occurring outside of genes\cite{Halligan:2013ir}.
Future comparative analyses using a common statistical framework (e.g. \cite{corbett2015} )and considering additional ecological and life history factors (c.f. \cite{leffler2012}) should allow explicit testing of this idea.

\subsection*{Demography influences the efficiency of purifying selection} 
One of our more striking findings is that the impact of purifying selection on maize and teosinte qualitatively changed over time. 
We observe a more pronounced decrease in $\pi$ around genes in teosinte than maize (Figure \ref{fig:purify}A), but the opposite trend when we evaluate diversity using singleton polymorphisms (Figure \ref{fig:purify}B).
The efficiency of purifying selection is proportional to effective population size \cite{kimura1984}, and these results are thus consistent with our demographic analyses which show a domestication bottleneck and smaller long-term $N_e$ in maize \cite{eyre1998, tenaillon2004, wright2005, ross2009} followed by recent rapid expansion and a much larger modern $N_e$. 
Simple foward-in-time population genetic simulations qualitatively confirm these results, and further suggest that the observed patterns are likely cause by sites under relatively weak purifying selection \ref{sFig:sims}.

Although demographic change affects the efficiency of purifying selection, it may have limited implications for genetic load. 
Recent population bottlenecks and expansions have increased the relative abundance of rare and 
deleterious variants in domesticated plants \cite{Gunther:2010gt,renaut2015} and human populations out of Africa \cite{keinan2012,coventry2010}, and such variants may play an important role in phenotypic variation \cite{Mezmouk:2014es, coventry2010, eyre2010}.
Nonetheless, demographic history may have little impact on the overall genetic load of populations \cite{do2015,simons2014}, as decreases in $N_e$ that allow weakly deleterious variants to escape selection also help purge strongly deleterious ones, and the increase of new deleterious mutations in expanding populations is mitigated by their lower initial frequency and the increasing efficiency of purifying selection \cite{simons2014, lohmueller2014}.

@@

\section*{ACKNOWLEDGEMENTS}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014, the USDA-Agricultural Research Service, and USDA Hatch project CA-D-PLS-2066-H.
